Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-20 ms.tex
Reworking description of the instantaneous heating rate.

Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a
function of time $\tau_{\star}$ after a burst of star formation for a
black hole masses of $\Mbh = 10^{6} \Msun$.  These heating
rates are calculated using the stellar wind heating $v_{\rm
  w}^{\star}$ (Fig.~\ref{fig:vwImp}) and mass return parameter $\eta$
(Fig.~\ref{fig:eta}), the latter of which affects the other sources of
feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}],
[\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$;
eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$;
eq.~[\ref{eq:vIa}]).  The Ia heating rate also depends on a
convolution of the star formation history and the Ia delay-time
distribution (eq.~[\ref{eq:DTD}]).  At very early times ($\tau_{\star}
\lesssim XXX$), stellar wind heating dominates, but at later times
Compton heating dominates.  MSP heating is again found to be
negligible at all black hole masses.  Epochs of thermally-unstable
accretion are shown as a dashed line, indicating that Compton heating
becomes important only during the phase of unstable accretion.

From Figure~\ref{fig:vwSourcesImp} we conclude that thermally unstable accretion is the
norm.  However, a single burst of star formation does not describe the
average star formation histories of most galaxies.  Qualitatively,
smaller galaxies will on average have more recent star formation,
resulting in energetic young stellar winds and supernovae which
dominate the energy budget, resulting in a high heating rate of $\vwO
\sim 1000 $ km s$^{-1}$.  Massive galaxies, on the other hand, will on
average have older stellar populations, with their heating rates
dominated by Ia supernovae (on large radial scales) and SMBH feedback.
The average value of $\vwO$ is estimated as a function of SMBH mass
for each heating source by calculating its value using the average
cosmic star formation histories of \citet{MosterNaab+:2013a}.
Appendix \ref{app:windheat} describes how the average star formation
history is used to determine the stellar wind heating $v_{\rm
  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).

>>>>

Figure~\ref{fig:vwSourcesImp} shows the contributions of various
heating sources as a function of time $\tau_{\star}$ after a burst of
star formation for a black hole masses of $\Mbh = 10^{6} \Msun$ (top
panel) and $\Mbh = 10^{8} \Msun$ (bottom panel). The stellar wind
heating is calculated as described in appendix~\ref{app:windheat}. The
and Ia heating ($v_{w}^{\rm Ia}$) and compton heating ($v_{\rm
  w}^{\bullet}$) are calculated using equations~\eqref{eq:vIa}
and~\eqref{eq:vC} respectively. Both heating sources depend on the
value of the mass return parameter, $\eta$. We have plotted this for a
burst of star formation Figure~\ref{fig:etaImp}.  The Ia heating rate
also depends be a convolution of the delay time distribution
(eq. [\ref{eq:DTD}]) and the star formation history. This convolution
reduces to the delay time distribution itself for a burst of star
formation. To account for the non-steady nature of the Ia heating we
multiply the Ia heating by $e^{-\rs/\rIa}$, where $\rIa$ is the radius
where the time between subsequent supernovae is equal to the local
dynamical time. The heating contribiution from
Ia supernovae will be suppressed if the time between successive
supernovae is much greater than the dynamical time at $\rs$. Note that
both $v_{\rm w}^{\bullet}$ and $v_{\rm w}^{\rm Ia}$ depend on the
total heating rate (all of the heating sources added in quadrature),
and so we have to solve a system of impllicit eqautions for these.
The MSP contribution is negligible for both cases and is not plotted.

The overall heating rate declines with time and after some time the
flow would become thermally unstable. The epoch when this occurs is
shown by dashed lines in Figure~\ref{fig:vwSourcesImp}. In calculating
this transition we have not included the compton heating. However,
this would not be able stabilize flow as it would not respond
immediately to cooling instabilities. Thus, if Compton
heating is the dominant source of heating we do not expect a steady,
thermally stable flow. Thermal instability is the norm in the burst
limit except for very early times ($\lsim 10^7$ years) and small
$\Mbh$ ($\Mbh\simeq 10^6 \Msun$).

However, a single burst of star formation does not describe the
average star formation histories of most galaxies.  Qualitatively,
smaller galaxies will on average have more recent star formation,
resulting in energetic young stellar winds and supernovae which
dominate the energy budget, resulting in a high heating rate of $\vwO
\sim 1000 $ km s$^{-1}$.  Massive galaxies, on the other hand, will on
average have older stellar populations, with their heating rates
dominated by Ia supernovae (on large radial scales) and SMBH feedback.
The average value of $\vwO$ is estimated as a function of SMBH mass
for each heating source by calculating its value using the average
cosmic star formation histories of \citet{MosterNaab+:2013a}.
Appendix \ref{app:windheat} describes how the average star formation
history is used to determine the stellar wind heating $v_{\rm
  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).
